---
title: "R Notebook"
output: html_notebook
---

```{r, warning=FALSE}
library(tidyverse)
library(ggplot2)
library(lme4)
```

Read data of different years
```{r}
finaldf <- read.csv("combineddf.csv")
finaldf %>% head()
```

Print number of parcels
```{r}
finaldf %>% dim()
```

Check for NAs in the LIVING_AREA column.
There are $20000$ rows with NAs, out of over $1$ million rows. 
```{r}
finaldf %>% dplyr::filter(is.na(LIVING_AREA)) %>% nrow()
```

We remove rows with NAs in LIVING_AREA.
```{r}
finaldf <- finaldf %>% dplyr::filter(!is.na(LIVING_AREA))
```

Distribution of living area grouped by land usage.
For the "A" and "RL" categories, there are properties with living area $1$, which 
must be systematically wrong.
```{r}
p <- finaldf %>% ggplot(aes(x=LIVING_AREA)) + geom_histogram() +
  facet_wrap(vars(LU), scales="free")
p
```
Find extremes of living areas.
Even filtering out parcels with positive living area,
there are still parcels with living area $1$.
```{r}
finaldf %>% dplyr::filter(LIVING_AREA > 0) %>%
  group_by(LU) %>% 
  summarize(maxval = max(LIVING_AREA), minval = min(LIVING_AREA))
```

Focus on individual land use codes.
For code R4, by filtering out living area more than $1$, we have living areas
of one order of magnitude.
```{r}
finaldf %>% 
  dplyr::filter(LIVING_AREA > 1) %>%
  dplyr::filter(LU == "R4") %>% arrange(LIVING_AREA)
```

Check if filtering living area works for other land use codes.
There are "A" codes that have the wrong entries for living are, such as 
PID 1101661000, but the total value has been consistently updated (from 2015 through 2018),
and the total value hsa been increasing. 
```{r}
finaldf %>% 
  dplyr::filter(LIVING_AREA > 1) %>% 
  arrange(LIVING_AREA)
```


Filter out parcels with less than $300$ square feet living area.
For all the residential codes, $300$ square feet is a reasonable amount of living space.
We do this to remove parcels that have unreliable records of living area.
This retains most of the parcels (1302048 out of 1371391).
```{r}
threshold <- 300
finaldf <- finaldf %>% dplyr::filter(LIVING_AREA > threshold) 

finaldf %>% nrow()
```

Distribution of living area.
Discard the RL (residential lot) category.
As we move from CD -> R1 -> R2 -> R3 -> R4 -> A, the mass
of the log living area variable shifts to the right, which is in agreement
with the expectation that residential parcels for more families should have more
living area. 
```{r}
p <- finaldf %>% 
  dplyr::filter(LU != "RL") %>%
  ggplot(aes(x=log(LIVING_AREA), color=LU)) + geom_density(aes(fill=LU), alpha = 0.4) 
p
```